% This file contains the FRONT MATTER other than the title page

\tableofcontents

\chapter{Abstract}

For twelve thousand years the Galactic Empire has ruled supreme. Now it is dying. But only Hari Seldon, creator of the revolutionary science of psychohistory, can see into the future -- to a dark age of ignorance, barbarism, and warfare that will last thirty thousand years. To preserve knowledge and save mankind, Seldon gathers the best minds in the Empire -- both scientists and scholars -- and brings them to a bleak planet at the edge of the Galaxy to serve as a beacon of hope for a future generations. He calls his sanctuary the Foundation.

But soon the fledgling Foundation finds itself at the mercy of corrupt warlords rising in the wake of the receding Empire. Mankind's last best hope is faced with an agonizing choice: submit to the barbarians and be overrun -- or fight them and be destroyed.


\chapter{Preface}

\tocless\section{Statement of Originality}
The work contained in this thesis has not been previously submitted for a degree or diploma at any other higher education institution. %
To the best of my knowledge and belief, the thesis contains no material previously published or written by another person except where due references are made. %

\tocless\section{Ethical Approval}
This research was classed as `Type I' and did not require ethics approval. Confirmation of the activities to be undertaken as part of this thesis and a signed Research Ethics Form was submitted to the School in January 2016 . %

\tocless\section{Funding}
Include details of grants received here
\begin{itemize}
\item XXXXXXXXX: \pounds5,000
\item YYYYYYYYY: \pounds1,000
\item ZZZZZZZZZ: \pounds1,400
\end{itemize}

\tocless\section{Publications}
Details of chapters that have been published here. %

\chapter{Acknowledgements}

Thank you, thank you, thank you


% If you have no tables, delete the next line

\listoftables


% If you have no figures, delete the next line

\listoffigures


% Consult Ch 9 of the memoir class manual on how to set up other
% content lists. Note that memoir does not automatically clear the
% page for these. ucalgmthesis fixes this for the default table of
% contents and lists of tables and figures, but not for anything you
% define
